%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin]{resume}

\textwidth=145mm
%\textwidth=154mm
\itemsep=0cm
\parsep=0cm
\oddsidemargin -5mm
\evensidemargin -5mm
\topmargin -5mm
\textheight 235mm

%______________________________________________________________________________________________________________________
\begin{document}
\name{\large Radhika P Vasudevan}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Details}

    \textbf{Address}: 26 Heath Road \#4, Arlington MA 02474  \hfill \textbf{Phone}: (617)901-9049  \\ \textbf{Email}: radhika.pv@gmail.com         \\
    \textbf{LinkedIn}: https://www.linkedin.com/in/radhika-p-vasudevan-17a76431\\

			\vspace{-5mm}
    %__________________________________________________________________________________________________________________
    % Interests
    \section{\mysidestyle Experience \\ Summary}
		\begin{list2}
    \item Over 6 years of IT experience involving design, development and other stages in software development life cycle
    \item Excellent communication and interpersonal skills with a strong sense of team spirit
    \item Outstanding debugging skills and proficient in finding the root cause of problems
    \item Ability to quickly decipher existing code bases
		\item Ability to work under aggressive deadlines and handle multiple tasks simultaneously
		\end{list2}

    \section{\mysidestyle Skills}
		Java, Solaris, Linux, HP-UX, Shell scripting, PostgreSQL, JIDE, ClearCase, EMS/NMS, HTML, MySQL, Oracle, Flex

\section{\mysidestyle Experience}
\textbf{Lead Engineer, HCL Technologies}, Chennai, India \hfill \textbf{\textit{Aug 2013 -- Nov 2015}}\\
\vspace{-10pt}
\begin{list2}
\item Developed Database Migration Verifier tool from scratch. It is a
diff-tool for databases which takes in a configurable inclusion/exclusion list
for comparison. It resulted in reducing the functional failures of
\textbf{Brocade Network Advisor}, leading to enormous cost savings.
\item Owned the dashboard module of the Brocade Network Advisor, which displays
various network element monitors, and designed an efficient algorithm to place
differently sized components in the layout using JIDE.
\item Involved in the enhancement and maintenance of the Brocade Network
Advisor's client module.
\end{list2}
	
\textbf{Project Engineer, Wipro Technologies}, Chennai, India \hfill \textbf{\textit{June 2011 -- July 2013}}\\
\vspace{-10pt}
\begin{list2}\item
Involved in the development of a software upgrade manager to automate the
upgrade process of network elements managed by the EMS (OMEA), resulting in
huge time savings by eliminating the need to upgrade individual nodes or keep
track of the progress manually. Some of my roles were to develop the Remote
Method Invocation interfacing with OMEA and the GUI front-end.
\end{list2}

\textbf{Project Engineer, Wipro Technologies}, Bangalore, India \hfill \textbf{\textit{Nov 2009 -- May 2011}}\\
\vspace{-10pt}
\begin{list2}\item
Involved in the development of tools for packaging, installation,
configuration, process management, backup and restore, and upgrade
functionality within Nortel's OSR product suite using a combination of shell
scripts, java applications and other third party tools. In particular, used
Solaris' Service Management Facility for process management.
\end{list2}

\section{\mysidestyle Honors and Awards}
\begin{list2}

\item Green Belt Certification, HCL Technologies, April 2015, awarded for
significant cost reduction caused by the Database Migration Verifier Tool.

\item Outstanding Team Performer, HCL Technologies, January 2015, awarded for the
best performer in the team for the quarter.

\item Top Coder Award, HCL Technologies, October 2014, awarded for outstanding
code development.

\item Thanks A Zillion Award, Wipro Technologies, February 2013, awarded for
outstanding code contribution.

\item Topper Award, Wipro Technologies, October 2009, awarded to the top two
trainees.

\end{list2}

\section{\mysidestyle Education}
\textbf{B.Tech, IT (Information Technology), Anna University, India} \hfill \textit{Aug 2004 -- July 2008}\\

\section{\mysidestyle Languages Known}
English, Tamil, Hindi, Kannada, French

\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

